---
title: "Data_visualization_coursework"
output: html_document
date: "2022-09-15"
---
This coursework is about using the designated datasets to do relevant data visualization and animation. This Rmd file and the generated gif files are my own work. Please do not distribute them without my permission.

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = FALSE)
library(ggplot2)
library(gganimate)
library(gapminder)
```

Show the relationship between gdp per capital and the life expectancy
```{r cars}
# default plot
p1 <- 
  ggplot(
  gapminder, 
  aes(x = gdpPercap, y=lifeExp, size = pop, colour = country)
  ) +
  geom_point(show.legend = FALSE, alpha = 0.7) +
  scale_color_viridis_d() +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  labs(x = "GDP per capita", y = "Life expectancy")
# animate it
p1 + transition_time(year) +
  labs(title = "Year: {frame_time}")
anim_save("life_expectancy1.gif")
# show changes in different continents
p1 + facet_wrap(~continent) +
  transition_time(year) +
  labs(title = "Year: {frame_time}")
anim_save("life_expectancy2.gif")
```

Using airquality data to show the change of the temperature in a day.
```{r}
# default plot
p2 <- 
  ggplot(
  airquality,
  aes(Day, Temp, group = Month, color = factor(Month))
  ) +
  geom_line() +
  scale_color_viridis_d() +
  labs(x = "Day of Month", y = "Temperature") +
  theme(legend.position = "top")
p2
# animate it
p2 + transition_reveal(Day)
anim_save("temperature1.gif")
# show changes in different months
p2 + 
  transition_reveal(Day) +
  facet_wrap(~Month)
anim_save("temperature2.gif")
```

Using the same dataset to show the change of the average temperature in different months.
```{r}
# data preparation
mean.temp <- airquality %>%
  group_by(Month) %>%
  summarise(Temp = mean(Temp))
mean.temp
# default plot
p3 <- ggplot(mean.temp, aes(Month, Temp, fill = Temp)) +
  geom_col() +
  scale_fill_distiller(palette = "Reds", direction = 1) +
  theme_minimal() +
  theme(
    panel.grid = element_blank(),
    panel.grid.major.y = element_line(color = "white"),
    panel.ontop = TRUE
  )
p3
# animate the bar plot
p3 + transition_states(Month, wrap = FALSE) +
  shadow_mark()
anim_save("temperature3.gif")
```

